\textit{Supplementary materials for}: Text embedding models yield high-resolution insights into conceptual knowledge from short multiple-choice quizzes

### 2023-10-24 paper/supplement.tex
filled in supplemental materials captions, updated word overlap comparison figure highlights.  also re-regenerated and compiled the track-changes pdf and updated old.tex using the prior submission of our paper.

    \caption{\textbf{Table title.} Caption content caption content caption content caption content caption content caption content caption content caption content caption content caption content.}
    \end{longtable}
\end{tiny}

@@

    \caption{\textbf{Figure title}. Figure caption figure caption figure caption figure caption figure caption figure caption figure caption figure caption figure caption figure caption figure caption figure.}

    \label{fig:forces-peaks}
\end{figure}

@@

    \caption{\textbf{Figure title}. Figure caption figure caption figure caption figure caption figure caption figure caption figure caption figure caption figure caption figure caption figure caption figure.}

@@

%\begin{figure}[tp]
%    \centering
%    \includegraphics[width=\textwidth]{figs/word-overlap-comparison-v2}
%
%    \caption{\textbf{Figure title}. Figure caption figure caption figure caption figure caption figure caption figure caption figure caption figure caption figure caption figure caption figure caption figure.}
%
%    \label{fig:compare-wordcount}
%\end{figure}

\begin{figure}[tp]
    \centering
    \includegraphics[width=0.8\textwidth]{figs/model-comparison}

    \caption{\textbf{Figure title}. Figure caption figure caption figure caption figure caption figure caption figure caption figure caption figure caption figure caption figure caption figure caption figure.}

>>>>

\caption{\textbf{Lecture-specific questions and lecture excerpts.} We used the
text embeddings of each question about \textit{Four Fundamental Forces} (FFF)
and \textit{Birth of Stars} to identify corresponding matching intervals of the
lectures. The text of the questions and the best-matching time intervals of the
lecture transcripts are displayed (lecture times are noted in square brackets).
Timecourses of topic correlations for each question may be found in
Supplemntary Figures~\ref{fig:forces-peaks} and~\ref{fig:bos-peaks}. Note that
no matching lecture interval was found for Question 29.} 
\label{tab:matches}
\end{longtable}
\end{tiny}

@@

    \caption{\textbf{Topic correlation timeseries plots for individual
    \textit{Four Fundamental Forces} questions}. Each panel displays a
    timeseries plot showing how the question's topic vector correlates with the
    topic vectors for each timepoint of \textit{Four Fundamental Forces}. The
    shaded regions in each curve denote the full width at half maximum (FWHM)
    of the peak(s) in the curve. These FWHM intervals were used to identify the
    corresponding lecture intervals displayed in Supplementary
    Table~\ref{tab:matches}. The diamonds denote the peak correlation values
    (local maxima) within each shaded region.}
    \label{fig:forces-peaks}
\end{figure}

@@

    \caption{\textbf{Topic correlation timeseries plots for individual
    \textit{Birth of Stars} questions}. Each panel displays a
    timeseries plot showing how the question's topic vector correlates with the
    topic vectors for each timepoint of \textit{Birth of Stars}. The
    shaded regions in each curve denote the full width at half maximum (FWHM)
    of the peak(s) in the curve. These FWHM intervals were used to identify the
    corresponding lecture intervals displayed in Supplementary
    Table~\ref{tab:matches}. The diamonds denote the peak correlation values
    (local maxima) within each shaded region.}

@@

\begin{figure}[tp]
    \centering
    \includegraphics[width=0.57\textwidth]{figs/word-overlap-comparison}

    \caption{\textbf{Topic correlations versus word overlap}. \textbf{A.
    Single-timepoint comparisons for \textit{Four Fundamental Forces}.} Each
    question about \textit{Four Fundamental Forces} was compared to each
    timepoint of the lecture (dots). The blue dots denote the correlations
    between the topic vectors, and the orange dots denote Jaccard similarities
    (defined as the number of unique words in common between the question and
    corresponding window of the lecture, divided by the total number of unique
    words in both). \textbf{B. Single-timepoint comparisons for \textit{Birth
    of Stars}. Same format as Panel A. \textbf{C. Topic correlation timeseries
    plots.} This panel is in the same format as Figure 4A from the main text,
    but here the example question highlighted in purple in Panel A has been
    emphasized for the \textit{Four Fundamental Forces} traces on the left, and
    the example question highlighted in green in Panel B has been emphasized
    for the \textbf{Birth of Stars} traces on the right. \textbf{D. Jaccard
    similarity timeseries plots.} These panels are in the same format as Panel
    C, but they display the Jaccard similarity timeseries for the same
    questions. \textbf{E. Question and lecture text.} The text for the example
    purple (left) and green (right) questions is shown on top, and the text
    from the best-matching intervals of the lectures (computed using topic
    correlations; see Supp. Tab.~\ref{tab:matches}) are shown on the bottom.}}

    \label{fig:compare-wordcount}
\end{figure}

\begin{figure}[tp]
    \centering
    \includegraphics[width=0.7\textwidth]{figs/model-comparison}

    \caption{\textbf{Comparing LDA vs. BERT embeddings}. The rows of the
    display the equivalents of Figures 2C (top row), 4A and B (middle two
    rows), and 3B (bottom row) computed using LDA (left) and BERT (right).}
